---
title: "schedule-h-rdb-table.rmd"
author: "Qingqing"
date: "2019/6/26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library( xmltools )
library( purrr )
library( xml2 )
library( XML )
library( dplyr )
library( pander )

```


```{r}
lehigh <-
"<LEHIGH>   
<ManagementCoAndJntVenturesGrp>
        <EntityName>
          <BusinessNameLine1Txt>1 LVHN RECIPROCAL RISK RETENTION GROUP</BusinessNameLine1Txt>
        </EntityName>
        <PrimaryActivitiesTxt>MALPRACTICE INSURANCE</PrimaryActivitiesTxt>
        <OrgProfitOrOwnershipPct>0.11110</OrgProfitOrOwnershipPct>
        <OfcrEtcProfitOrOwnershipPct>0.00000</OfcrEtcProfitOrOwnershipPct>
        <PhysiciansProfitOrOwnershipPct>0.00000</PhysiciansProfitOrOwnershipPct>
      </ManagementCoAndJntVenturesGrp>
      <ManagementCoAndJntVenturesGrp>
        <EntityName>
          <BusinessNameLine1Txt>2 HEALTH NETWORK LABORATORIES LLC</BusinessNameLine1Txt>
        </EntityName>
        <PrimaryActivitiesTxt>LABORATORY SERVICES</PrimaryActivitiesTxt>
        <OrgProfitOrOwnershipPct>0.83240</OrgProfitOrOwnershipPct>
        <OfcrEtcProfitOrOwnershipPct>0.00000</OfcrEtcProfitOrOwnershipPct>
        <PhysiciansProfitOrOwnershipPct>0.00000</PhysiciansProfitOrOwnershipPct>
      </ManagementCoAndJntVenturesGrp>
      <ManagementCoAndJntVenturesGrp>
        <EntityName>
          <BusinessNameLine1Txt>3 HEALTH NETWORK LABORATORIES LP</BusinessNameLine1Txt>
        </EntityName>
        <PrimaryActivitiesTxt>LABORATORY SERVICES</PrimaryActivitiesTxt>
        <OrgProfitOrOwnershipPct>0.81540</OrgProfitOrOwnershipPct>
        <OfcrEtcProfitOrOwnershipPct>0.00000</OfcrEtcProfitOrOwnershipPct>
        <PhysiciansProfitOrOwnershipPct>0.00000</PhysiciansProfitOrOwnershipPct>
      </ManagementCoAndJntVenturesGrp>
      <ManagementCoAndJntVenturesGrp>
        <EntityName>
          <BusinessNameLine1Txt>4 LEHIGH VALLEY PHYSICIAN HOSPITAL ORGANIZATION INC</BusinessNameLine1Txt>
        </EntityName>
        <PrimaryActivitiesTxt>HEALTH CARE SERVICES</PrimaryActivitiesTxt>
        <OrgProfitOrOwnershipPct>0.45000</OrgProfitOrOwnershipPct>
        <OfcrEtcProfitOrOwnershipPct>0.00000</OfcrEtcProfitOrOwnershipPct>
        <PhysiciansProfitOrOwnershipPct>0.00000</PhysiciansProfitOrOwnershipPct>
      </ManagementCoAndJntVenturesGrp>
</LEHIGH>"

```

```{r}
doc <- xml2::read_xml( lehigh )
nodeset <- xml2::xml_children( doc ) # top level nodeset
xmltools::xml_view_trees( doc )
```

```{r}
doc <- xml2::read_xml( lehigh )


# nodeset is a group of nodes returned
# from the previous step
nodeset_to_df <- function( nodeset )
{
  node_to_df <- function(x)
  { 
    vec <- xml_text(xml_children(x))
    names(vec) <- xml_name(xml_children(x)) 
    df <- data.frame( as.list( vec ), stringsAsFactors=F )
    return( df )
  }
  
  node.list <- lapply( nodeset, node_to_df )
  df <- bind_rows( node.list )
  return( df )
}

# xml2::xml_structure( doc )
# nodeset <- xml2::xml_children( doc )
# nodeset_to_df( nodeset )

```

```{r}
group.name.3 <- "//Form990ScheduleHPartIV"
group.name.4 <- "//ManagementCoAndJntVenturesGrp"
all.versions <- paste( group.name.3, group.name.4, sep="|" )


# leigh hospital 
M3 <- "https://s3.amazonaws.com/irs-form-990/201801319349300130_public.xml"
doc <- read_xml( M3 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
nodeset_to_df( node.group ) %>% pander()

```
# Load Concordance File


```{r}
# load concordance for schedule h
dropbox.url <- "https://www.dropbox.com/s/k2tohl0ik4odjii/schedule-h-v1.csv?dl=1"
sh <- read.csv( dropbox.url, stringsAsFactors=F )

# remove leading forward slash
# though we need to add it back below
xpaths <- sh$xpath 
xpaths <- gsub( "/Return/", "Return/", xpaths )
```

## Get xpaths for Each RDB Table

```{r}
table( sh$rdb_table )

xpaths.t1 <- xpaths[ sh$rdb_table == "SH-TABLE-01-COMPANY-JOINT-VENTURES" ]
xpaths.t2 <- xpaths[ sh$rdb_table == "SH-TABLE-02-HOSPITAL-FACILITY" ]
xpaths.t3 <- xpaths[ sh$rdb_table == "SH-TABLE-03-OTHER-CARE-FACILITY" ]
xpaths.t4 <- xpaths[ sh$rdb_table == "SH-TABLE-04-SUPPL-INFO" ]
```



## Compare xpath Levels # imortant steps 

```{r}
nodes <- strsplit( xpaths.t1, "/" )

xpath.levels <- sapply( nodes, length )
max.lev <- max( xpath.levels )
nodes <- lapply( nodes, function(x){ c(x, rep("",max.lev-length(x) ) ) } )

# compare xpath levels
xpath.levels <- data.frame( do.call( cbind, nodes ), stringsAsFactors=F )
xpath.levels[ , 1:10 ] %>% pander
```



# Identify Group Levels


## Find Grouping Variables

This one works well but only works on active xpaths in a specific XML document. We can't use it with the list of raw xpaths from the concordance file.

```{r}
## we can identify grouping variables
doc <- xml2::read_xml( lehigh )

## get all xpaths
all.xpaths <- doc %>%  xml_get_paths()

## collapse xpaths to unique only
unique.xpaths <- all.xpaths %>%
  unlist() %>%
  unique()

## but what we really want is the parent node of terminal nodes.
## use the `only_terminal_parent = TRUE` to do this

## get all xpaths to parents of parent node
groups.all <- doc %>% 
  xml_get_paths( only_terminal_parent = TRUE )

## collapse xpaths to unique only
groups <- groups.all %>% 
  unlist() %>%
  unique()

groups
```

This will return all variables at the first level where the nodes split. Some will be grouping variables, and some will be regular variables. Have to inspect to see. （ this is useful)

*I need to improve this to return only grouping variables, if possible.*

```{r}
find_group_name <- function( xpaths )
{
  nodes <- strsplit( xpaths, "/" )
  d1 <- data.frame( do.call( cbind, nodes ), stringsAsFactors=F )
  not.equal <- apply( d1, MARGIN=1, FUN=function(x){ length( unique( x )) > 1 } ) 
  this.one <- which( not.equal == T )[ 1 ]
  group.names <- d1[ this.one,  ] %>% as.character() %>% unique()
  return( group.names )
}

find_group_name( xpaths.t1 )  
```



## Sample data from Schedule H Part IV 
```{r}

group.name.3 <- "//Form990ScheduleHPartIV"
group.name.4 <- "//ManagementCoAndJntVenturesGrp"
all.versions <- paste( group.name.3, group.name.4, sep="|" )

#READING HOSPITAL# skip column d #1orgs
M1 <- "https://s3.amazonaws.com/irs-form-990/201821039349300712_public.xml"

#ABINGTON MEMORIAL HOSPITAL# skip column d #5 orgs
M2 <-  "https://s3.amazonaws.com/irs-form-990/201831359349306048_public.xml"

#LEHIGH VALLEY HOSPITAL # 4 orgs 
M3 <- "https://s3.amazonaws.com/irs-form-990/201801319349300130_public.xml"


#Charlotte Hungerford Hospital# skip column d # 2 orgs
M4 <- "https://s3.amazonaws.com/irs-form-990/201802259349302005_public.xml"


# fill none in the first row and the first two column #1 org
M5 <- "https://s3.amazonaws.com/irs-form-990/201832259349301448_public.xml"


# grady hospital does not contain part IV 
M6 <- "https://s3.amazonaws.com/irs-form-990/201813189349303776_public.xml"



list.of.tables <- list()

doc <- read_xml( M1 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[1]] <- nodeset_to_df( node.group )

doc <- read_xml( M2 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[2]] <- nodeset_to_df( node.group )

doc <- read_xml( M3 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[3]] <- nodeset_to_df( node.group )

doc <- read_xml( M4 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[4]] <- nodeset_to_df( node.group )

doc <- read_xml( M5 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[5]] <- nodeset_to_df( node.group )

doc <- read_xml( M6 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[6]] <- nodeset_to_df( node.group )


# list.of.tables

#bind_rows( list.of.tables ) 


# list.of.tables

managementAndjointventure <- bind_rows( list.of.tables ) 
#write.csv(managementAndjointventure, "managementAndjointventure.csv")


```




```{r}
# hypoethetical build file does not work

# node groups for Sched-H Part V
group.name.3 <- "//Form990ScheduleHPartIV"
group.name.4 <- "//ManagementCoAndJntVenturesGrp"
all.versions <- paste( group.name.3, group.name.4, sep="|" )

dat <- readRDS( gzcon( url( "https://www.dropbox.com/s/4ptsnryf64vkqlg/2016-EFILE-CORE.rds?dl=1" ) ) )

# find likely schedule H filers
dat.h <- dat[ grepl( "HOSPITAL", dat$NAME ) , ]
hospitals <- head( dat.h$URL )


i.counter <- 1

sched.h.part.v <- list()

for( i in hospitals$URL )
{
  doc <- read_xml( i ) %>% xml_ns_strip()
  node.group <- xml_find_all( doc, all.versions )
  sched.h.part.v [[ i.counter ]] <- nodeset_to_df( node.group )
  
  i.counter <- i.counter + 1
}


```