---
title: "Schedule D Part V"
date: "June 26, 2019"
output:
  html_document:
    theme: readable
    df_print: paged
    highlight: tango
    smart: false
    toc: yes
    toc_float: no
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set( echo=TRUE, message=F, warning=F, fig.width=10 )
```


```{css, echo=F}
h1, h2{
  margin-top:100px;
  margin-bottom:20px;
}

table
{ 
    margin-left: auto;
    margin-right: auto;
    margin-top:80px;
    margin-bottom:800px;
}

img {
    max-width: 90%;
    display: block;
    margin-right: auto;
    margin-left: auto;
    margin-top:30px;
    margin-bottom:20px;
}
```



```{r}
library( dplyr )
library( pander )
library( xml2 )
```




# Build Chunks from Concordance


```{r}
# load concordance file
cf <- read.csv("https://www.dropbox.com/s/omi8qu3owcbn8gc/schedule-d-partv-v0.csv?dl=1",
               stringsAsFactors=F )
head( cf )
```




```{r, eval=F}
create_code_chunks <- function( dat, function.name="buildFUNCTION" )
{

  library( dplyr )
  
  names(dat) <- toupper( names(dat) )
  dat$VARIABLE_NAME <- gsub( "-", "_", dat$VARIABLE_NAME ) 
  
  file.create( "CodeChunks.txt" )
  fileConn <- file( "CodeChunks.txt", open="a" )


  #-------------------------------------------------------------------

  writeLines( paste0( function.name, " <- function( doc, url )" ), con = fileConn, sep = "\n" )
  writeLines( "{", con = fileConn, sep = "\n\n\n" )
  writeLines( "## NAME", con = fileConn, sep = "\n\n" )
  writeLines( "V_990NAMEpost2014 <- \"//Return/ReturnHeader/Filer/BusinessName/BusinessNameLine1Txt\" ", con = fileConn, sep = "\n" )
  writeLines( "V_990NAME_2013 <- \"//Return/ReturnHeader/Filer/BusinessName/BusinessNameLine1\" ", con = fileConn, sep = "\n" )
  writeLines( "V_990NAMEpre2013  <- \"//Return/ReturnHeader/Filer/Name/BusinessNameLine1\"", con = fileConn, sep = "\n" )
  writeLines( "name.xpath <- paste( V_990NAME_2013, V_990NAMEpre2013, V_990NAMEpost2014, sep=\"|\" )", con = fileConn, sep = "\n" )
  writeLines( "NAME <- xml_text( xml_find_all( doc, name.xpath ) )", con = fileConn, sep = "\n\n" )
  writeLines( "## EIN", con = fileConn, sep = "\n" )
  writeLines( "EIN  <- xml_text( xml_find_all( doc, \"//Return/ReturnHeader/Filer/EIN\" ) )", con = fileConn, sep = "\n\n" )
  writeLines( "## TAX YEAR", con = fileConn, sep = "\n" )
  writeLines( "V_990FYRpost2013 <- \"//Return/ReturnHeader/TaxYr\"", con = fileConn, sep = "\n" )
  writeLines( "V_990FYRpre2013  <- \"//Return/ReturnHeader/TaxYear\"", con = fileConn, sep = "\n" )
  writeLines( "tax.year.xpath <- paste( V_990FYRpost2013, V_990FYRpre2013, sep=\"|\" )", con = fileConn, sep = "\n" )
  writeLines( "TAXYR <- xml_text( xml_find_all( doc, tax.year.xpath ) )", con = fileConn, sep = "\n\n" )
  writeLines( "## TYPE OF TAX FORM", con = fileConn, sep = "\n" )
  writeLines( "V_990TFpost2013 <- \"//Return/ReturnHeader/ReturnTypeCd\"", con = fileConn, sep = "\n" )
  writeLines( "V_990TFpre2013  <- \"//Return/ReturnHeader/ReturnType\"", con = fileConn, sep = "\n" )
  writeLines( "tax.form.xpath <- paste( V_990TFpost2013, V_990TFpre2013, sep=\"|\" )", con = fileConn, sep = "\n" )
  writeLines( "FORMTYPE <- xml_text( xml_find_all( doc, tax.form.xpath ) )", con = fileConn, sep = "\n\n" )
  writeLines( "## OBJECT ID", con = fileConn, sep = "\n" )
  writeLines( "OBJECTID <- get_object_id( url )", con = fileConn, sep = "\n\n" )
  writeLines( "## URL", con = fileConn, sep = "\n" )
  writeLines( "URL <- url", con = fileConn, sep = "\n\n" )
  writeLines( "#-------------------------------------------------------------------", con = fileConn, sep = "\n\n\n" )

  


  for( i in unique( dat$VARIABLE_NAME ) )
  {

     sub.dat <- dat[ dat$VARIABLE_NAME == i , ]

     writeLines( paste("## VARIABLE NAME: ", i), con = fileConn, sep = "\n" )
     writeLines( paste("## DESCRIPTION: ", sub.dat$DESCRIPTION[1]), con = fileConn, sep = "\n" )
     writeLines( paste("## LOCATION: ", sub.dat$LOCATION_CODE[1]), con = fileConn, sep = "\n" )
     writeLines( paste("## TABLE: ", sub.dat$RDB_TABLE[1]), con = fileConn, sep = "\n" )
     writeLines( paste("## VARIABLE TYPE: ", sub.dat$DATA_TYPE_SIMPLE[1]), con = fileConn, sep = "\n\n" )


     xpath.vec <- sub.dat$XPATH

     num.paths <- length( xpath.vec )


     if( num.paths > 1 ){

     for( j in 1:num.paths )
     {
       xpath.j <- paste( "V", j, sep="" )
       writeLines( paste( xpath.j, " <- '/", xpath.vec[j], "'", sep=""), con = fileConn, sep = "\n" )

     }
      or.var.name <- substr( i, 10, nchar(i) )
      or.statement <- paste( or.var.name, "<- paste(", paste( "V", 1:num.paths, sep="", collapse=", " ), ", sep='|' )" ) 
      writeLines( or.statement, con = fileConn, sep = "\n" )
      writeLines( paste( i, "<- xml_text( xml_find_all( doc,", or.var.name, ") )"), con = fileConn, sep = "\n\n\n\n\n\n" )

      } else
      {

        single.xpath <- paste( "'", xpath.vec, "'", sep="" )
        writeLines( paste( i, "<- xml_text( xml_find_all( doc,", single.xpath, ") )"), con = fileConn, sep = "\n\n\n\n\n\n" )

      }
  }

  
  var.names <- as.character( unique( dat$VARIABLE_NAME ) )


  writeLines(  "namedList <- function(...){
		      names <- as.list(substitute(list(...)))[-1L]
		      result <- list(...)
		      names(result) <- names
		      result[sapply(result, function(x){length(x)==0})] <- NA
		      result[sapply(result, is.null)] <- NA
		      result
		  }", , con = fileConn, sep = "\n\n" )

  
  writeLines( paste0( "d <- namedList( NAME, EIN, TAXYR, FORMTYPE, OBJECTID, URL, ", paste( var.names, collapse=", " ), " )" ), con = fileConn, sep = "\n\n" )  
  writeLines( "return( d )", con = fileConn, sep = "\n\n\n" ) 
  writeLines( "}", con = fileConn, sep = "\n" )   
  
  close( fileConn ) 
  
  shell( "CodeChunks.txt" )
  
  return( NULL )

}
```


```{r, eval=F}
create_code_chunks( cf )
```


```{r, eval=T}
buildFUNCTION <- function( doc, url )
{


## NAME

V_990NAMEpost2014 <- "//Return/ReturnHeader/Filer/BusinessName/BusinessNameLine1Txt" 
V_990NAME_2013 <- "//Return/ReturnHeader/Filer/BusinessName/BusinessNameLine1" 
V_990NAMEpre2013  <- "//Return/ReturnHeader/Filer/Name/BusinessNameLine1"
name.xpath <- paste( V_990NAME_2013, V_990NAMEpre2013, V_990NAMEpost2014, sep="|" )
NAME <- xml_text( xml_find_all( doc, name.xpath ) )

## EIN
EIN  <- xml_text( xml_find_all( doc, "//Return/ReturnHeader/Filer/EIN" ) )

## TAX YEAR
V_990FYRpost2013 <- "//Return/ReturnHeader/TaxYr"
V_990FYRpre2013  <- "//Return/ReturnHeader/TaxYear"
tax.year.xpath <- paste( V_990FYRpost2013, V_990FYRpre2013, sep="|" )
TAXYR <- xml_text( xml_find_all( doc, tax.year.xpath ) )

## TYPE OF TAX FORM
V_990TFpost2013 <- "//Return/ReturnHeader/ReturnTypeCd"
V_990TFpre2013  <- "//Return/ReturnHeader/ReturnType"
tax.form.xpath <- paste( V_990TFpost2013, V_990TFpre2013, sep="|" )
FORMTYPE <- xml_text( xml_find_all( doc, tax.form.xpath ) )

## OBJECT ID
OBJECTID <- get_object_id( url )

## URL
URL <- url

#-------------------------------------------------------------------


## VARIABLE NAME:  SD_05_PC_ARREORLISCR
## DESCRIPTION:  Are related orgs listed on Schedule R?
## LOCATION:  SCHED-D-PART-05-LINE-3b
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  checkbox

V1 <- '//Return/ReturnData/IRS990ScheduleD/AreRelatedOrgsListedScheduleR'
V2 <- '//Return/ReturnData/IRS990ScheduleD/Form990ScheduleDPartV/AreRelatedOrgsListedScheduleR'
V3 <- '//Return/ReturnData/IRS990ScheduleD/RelatedOrgListSchRInd'
ARREORLISCR <- paste( V1, V2, V3 , sep='|' )
SD_05_PC_ARREORLISCR <- xml_text( xml_find_all( doc, ARREORLISCR ) )





## VARIABLE NAME:  SD_05_PC_BDBEOYPCT
## DESCRIPTION:  Board designated EOY balance
## LOCATION:  SCHED-D-PART-05-LINE-2a
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/BoardDesignatedBalanceEOYPct'
V2 <- '//Return/ReturnData/IRS990ScheduleD/BoardDesignatedEOYBalance'
V3 <- '//Return/ReturnData/IRS990ScheduleD/Form990ScheduleDPartV/BoardDesignatedEOYBalance'
BDBEOYPCT <- paste( V1, V2, V3 , sep='|' )
SD_05_PC_BDBEOYPCT <- xml_text( xml_find_all( doc, BDBEOYPCT ) )





## VARIABLE NAME:  SD_05_PC_CURYEAADMEXP
## DESCRIPTION:  Administrative expenses
## LOCATION:  SCHED-D-PART-05-LINE-1f
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYear/AdministrativeExpenses'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYEndwmtFundGrp/AdministrativeExpensesAmt'
V3 <- '//Return/ReturnData/IRS990ScheduleD/Form990ScheduleDPartV/CurrentYear/AdministrativeExpenses'
CURYEAADMEXP <- paste( V1, V2, V3 , sep='|' )
SD_05_PC_CURYEAADMEXP <- xml_text( xml_find_all( doc, CURYEAADMEXP ) )





## VARIABLE NAME:  SD_05_PC_CUYEBEOFYEBA
## DESCRIPTION:  Beginning of year balance
## LOCATION:  SCHED-D-PART-05-LINE-1a
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYear/AdministrativeExpenses'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYEndwmtFundGrp/BeginningYearBalanceAmt'
V3 <- '//Return/ReturnData/IRS990ScheduleD/Form990ScheduleDPartV/CurrentYear/BeginningOfYearBalance'
CUYEBEOFYEBA <- paste( V1, V2, V3 , sep='|' )
SD_05_PC_CUYEBEOFYEBA <- xml_text( xml_find_all( doc, CUYEBEOFYEBA ) )





## VARIABLE NAME:  SD_05_PC_CURRYEARCONT
## DESCRIPTION:  Current Year - Contributions
## LOCATION:  SCHED-D-PART-05-LINE-1b
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYear/Contributions'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYEndwmtFundGrp/ContributionsAmt'
V3 <- '//Return/ReturnData/IRS990ScheduleD/Form990ScheduleDPartV/CurrentYear/Contributions'
CURRYEARCONT <- paste( V1, V2, V3 , sep='|' )
SD_05_PC_CURRYEARCONT <- xml_text( xml_find_all( doc, CURRYEARCONT ) )





## VARIABLE NAME:  SD_05_PC_CUYEENOFYEBA
## DESCRIPTION:  End of year balance
## LOCATION:  SCHED-D-PART-05-LINE-1g
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYear/EndOfYearBalance'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYEndwmtFundGrp/EndYearBalanceAmt'
V3 <- '//Return/ReturnData/IRS990ScheduleD/Form990ScheduleDPartV/CurrentYear/EndOfYearBalance'
CUYEENOFYEBA <- paste( V1, V2, V3 , sep='|' )
SD_05_PC_CUYEENOFYEBA <- xml_text( xml_find_all( doc, CUYEENOFYEBA ) )





## VARIABLE NAME:  SD_05_PC_CUYEGRORSCCH
## DESCRIPTION:  Grants or scholarships
## LOCATION:  SCHED-D-PART-05-LINE-1d
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYear/GrantsOrScholarships'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYEndwmtFundGrp/GrantsOrScholarshipsAmt'
V3 <- '//Return/ReturnData/IRS990ScheduleD/Form990ScheduleDPartV/CurrentYear/GrantsOrScholarships'
CUYEGRORSCCH <- paste( V1, V2, V3 , sep='|' )
SD_05_PC_CUYEGRORSCCH <- xml_text( xml_find_all( doc, CUYEGRORSCCH ) )





## VARIABLE NAME:  SD_05_PC_CUYEINEAORLO
## DESCRIPTION:  Investment earnings or losses
## LOCATION:  SCHED-D-PART-05-LINE-1c
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYear/InvestmentEarningsOrLosses'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYEndwmtFundGrp/InvestmentEarningsOrLossesAmt'
V3 <- '//Return/ReturnData/IRS990ScheduleD/Form990ScheduleDPartV/CurrentYear/InvestmentEarningsOrLosses'
CUYEINEAORLO <- paste( V1, V2, V3 , sep='|' )
SD_05_PC_CUYEINEAORLO <- xml_text( xml_find_all( doc, CUYEINEAORLO ) )





## VARIABLE NAME:  SD_05_PC_CURYEAOTHEXP
## DESCRIPTION:  Other expenditures
## LOCATION:  SCHED-D-PART-05-LINE-1e
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYear/OtherExpenditures'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYEndwmtFundGrp/OtherExpendituresAmt'
V3 <- '//Return/ReturnData/IRS990ScheduleD/Form990ScheduleDPartV/CurrentYear/OtherExpenditures'
CURYEAOTHEXP <- paste( V1, V2, V3 , sep='|' )
SD_05_PC_CURYEAOTHEXP <- xml_text( xml_find_all( doc, CURYEAOTHEXP ) )





## VARIABLE NAME:  SD_05_PC_CUYEMIYEADEX1
## DESCRIPTION:  Administrative expenses
## LOCATION:  SCHED-D-PART-05-LINE-1f
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus1Year/AdministrativeExpenses'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus1YrEndwmtFundGrp/AdministrativeExpensesAmt'
CUYEMIYEADEX1 <- paste( V1, V2 , sep='|' )
SD_05_PC_CUYEMIYEADEX1 <- xml_text( xml_find_all( doc, CUYEMIYEADEX1 ) )





## VARIABLE NAME:  SD_05_PC_CYMYBOYBALAN1
## DESCRIPTION:  Beginning of year balance
## LOCATION:  SCHED-D-PART-05-LINE-1a
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus1Year/BeginningOfYearBalance'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus1YrEndwmtFundGrp/BeginningYearBalanceAmt'
CYMYBOYBALAN1 <- paste( V1, V2 , sep='|' )
SD_05_PC_CYMYBOYBALAN1 <- xml_text( xml_find_all( doc, CYMYBOYBALAN1 ) )





## VARIABLE NAME:  SD_05_PC_CUYEMIYECOON1
## DESCRIPTION:  Current Year Minus1 Year - Contributions
## LOCATION:  SCHED-D-PART-05-LINE-1b
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus1Year/Contributions'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus1YrEndwmtFundGrp/ContributionsAmt'
CUYEMIYECOON1 <- paste( V1, V2 , sep='|' )
SD_05_PC_CUYEMIYECOON1 <- xml_text( xml_find_all( doc, CUYEMIYECOON1 ) )





## VARIABLE NAME:  SD_05_PC_CYMYEOYBALAN1
## DESCRIPTION:  End of year balance
## LOCATION:  SCHED-D-PART-05-LINE-1g
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus1Year/EndOfYearBalance'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus1YrEndwmtFundGrp/EndYearBalanceAmt'
CYMYEOYBALAN1 <- paste( V1, V2 , sep='|' )
SD_05_PC_CYMYEOYBALAN1 <- xml_text( xml_find_all( doc, CYMYEOYBALAN1 ) )





## VARIABLE NAME:  SD_05_PC_CYMYGOSCHOLA1
## DESCRIPTION:  Grants or scholarships
## LOCATION:  SCHED-D-PART-05-LINE-1d
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus1Year/GrantsOrScholarships'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus1YrEndwmtFundGrp/GrantsOrScholarshipsAmt'
CYMYGOSCHOLA1 <- paste( V1, V2 , sep='|' )
SD_05_PC_CYMYGOSCHOLA1 <- xml_text( xml_find_all( doc, CYMYGOSCHOLA1 ) )





## VARIABLE NAME:  SD_05_PC_CYMYIEOLOSSE1
## DESCRIPTION:  Investment earnings or losses
## LOCATION:  SCHED-D-PART-05-LINE-1c
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus1Year/InvestmentEarningsOrLosses'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus1YrEndwmtFundGrp/InvestmentEarningsOrLossesAmt'
CYMYIEOLOSSE1 <- paste( V1, V2 , sep='|' )
SD_05_PC_CYMYIEOLOSSE1 <- xml_text( xml_find_all( doc, CYMYIEOLOSSE1 ) )





## VARIABLE NAME:  SD_05_PC_CUYEMIYEOTEX1
## DESCRIPTION:  Other expenditures
## LOCATION:  SCHED-D-PART-05-LINE-1e
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus1Year/OtherExpenditures'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus1YrEndwmtFundGrp/OtherExpendituresAmt'
CUYEMIYEOTEX1 <- paste( V1, V2 , sep='|' )
SD_05_PC_CUYEMIYEOTEX1 <- xml_text( xml_find_all( doc, CUYEMIYEOTEX1 ) )





## VARIABLE NAME:  SD_05_PC_CUYEMIYEADEX2
## DESCRIPTION:  Administrative expenses
## LOCATION:  SCHED-D-PART-05-LINE-1f
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus2Years/AdministrativeExpenses'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus2YrEndwmtFundGrp/AdministrativeExpensesAmt'
CUYEMIYEADEX2 <- paste( V1, V2 , sep='|' )
SD_05_PC_CUYEMIYEADEX2 <- xml_text( xml_find_all( doc, CUYEMIYEADEX2 ) )





## VARIABLE NAME:  SD_05_PC_CYMYBOYBALAN2
## DESCRIPTION:  Beginning of year balance
## LOCATION:  SCHED-D-PART-05-LINE-1a
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus2Years/BeginningOfYearBalance'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus2YrEndwmtFundGrp/BeginningYearBalanceAmt'
CYMYBOYBALAN2 <- paste( V1, V2 , sep='|' )
SD_05_PC_CYMYBOYBALAN2 <- xml_text( xml_find_all( doc, CYMYBOYBALAN2 ) )





## VARIABLE NAME:  SD_05_PC_CUYEMIYECOON2
## DESCRIPTION:  Current Year Minus2 Years - Contributions
## LOCATION:  SCHED-D-PART-05-LINE-1b
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus2Years/Contributions'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus2YrEndwmtFundGrp/ContributionsAmt'
CUYEMIYECOON2 <- paste( V1, V2 , sep='|' )
SD_05_PC_CUYEMIYECOON2 <- xml_text( xml_find_all( doc, CUYEMIYECOON2 ) )





## VARIABLE NAME:  SD_05_PC_CYMYEOYBALAN2
## DESCRIPTION:  End of year balance
## LOCATION:  SCHED-D-PART-05-LINE-1g
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus2Years/EndOfYearBalance'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus2YrEndwmtFundGrp/EndYearBalanceAmt'
CYMYEOYBALAN2 <- paste( V1, V2 , sep='|' )
SD_05_PC_CYMYEOYBALAN2 <- xml_text( xml_find_all( doc, CYMYEOYBALAN2 ) )





## VARIABLE NAME:  SD_05_PC_CYMYGOSCHOLA2
## DESCRIPTION:  Grants or scholarships
## LOCATION:  SCHED-D-PART-05-LINE-1d
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus2Years/GrantsOrScholarships'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus2YrEndwmtFundGrp/GrantsOrScholarshipsAmt'
CYMYGOSCHOLA2 <- paste( V1, V2 , sep='|' )
SD_05_PC_CYMYGOSCHOLA2 <- xml_text( xml_find_all( doc, CYMYGOSCHOLA2 ) )





## VARIABLE NAME:  SD_05_PC_CYMYIEOLOSSE2
## DESCRIPTION:  Investment earnings or losses
## LOCATION:  SCHED-D-PART-05-LINE-1c
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus2Years/InvestmentEarningsOrLosses'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus2YrEndwmtFundGrp/InvestmentEarningsOrLossesAmt'
CYMYIEOLOSSE2 <- paste( V1, V2 , sep='|' )
SD_05_PC_CYMYIEOLOSSE2 <- xml_text( xml_find_all( doc, CYMYIEOLOSSE2 ) )





## VARIABLE NAME:  SD_05_PC_CUYEMIYEOTEX2
## DESCRIPTION:  Other expenditures
## LOCATION:  SCHED-D-PART-05-LINE-1e
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus2Years/OtherExpenditures'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus2YrEndwmtFundGrp/OtherExpendituresAmt'
CUYEMIYEOTEX2 <- paste( V1, V2 , sep='|' )
SD_05_PC_CUYEMIYEOTEX2 <- xml_text( xml_find_all( doc, CUYEMIYEOTEX2 ) )





## VARIABLE NAME:  SD_05_PC_CUYEMIYEADEX3
## DESCRIPTION:  Administrative expenses
## LOCATION:  SCHED-D-PART-05-LINE-1f
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus3Years/AdministrativeExpenses'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus3YrEndwmtFundGrp/AdministrativeExpensesAmt'
CUYEMIYEADEX3 <- paste( V1, V2 , sep='|' )
SD_05_PC_CUYEMIYEADEX3 <- xml_text( xml_find_all( doc, CUYEMIYEADEX3 ) )





## VARIABLE NAME:  SD_05_PC_CYMYBOYBALAN3
## DESCRIPTION:  Beginning of year balance
## LOCATION:  SCHED-D-PART-05-LINE-1a
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus3Years/BeginningOfYearBalance'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus3YrEndwmtFundGrp/BeginningYearBalanceAmt'
CYMYBOYBALAN3 <- paste( V1, V2 , sep='|' )
SD_05_PC_CYMYBOYBALAN3 <- xml_text( xml_find_all( doc, CYMYBOYBALAN3 ) )





## VARIABLE NAME:  SD_05_PC_CUYEMIYECOON3
## DESCRIPTION:  Current Year Minus3 Years - Contributions
## LOCATION:  SCHED-D-PART-05-LINE-1b
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus3Years/Contributions'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus3YrEndwmtFundGrp/ContributionsAmt'
CUYEMIYECOON3 <- paste( V1, V2 , sep='|' )
SD_05_PC_CUYEMIYECOON3 <- xml_text( xml_find_all( doc, CUYEMIYECOON3 ) )





## VARIABLE NAME:  SD_05_PC_CYMYEOYBALAN3
## DESCRIPTION:  End of year balance
## LOCATION:  SCHED-D-PART-05-LINE-1g
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus3Years/EndOfYearBalance'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus3YrEndwmtFundGrp/EndYearBalanceAmt'
CYMYEOYBALAN3 <- paste( V1, V2 , sep='|' )
SD_05_PC_CYMYEOYBALAN3 <- xml_text( xml_find_all( doc, CYMYEOYBALAN3 ) )





## VARIABLE NAME:  SD_05_PC_CYMYGOSCHOLA3
## DESCRIPTION:  Grants or scholarships
## LOCATION:  SCHED-D-PART-05-LINE-1d
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus3Years/GrantsOrScholarships'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus3YrEndwmtFundGrp/GrantsOrScholarshipsAmt'
CYMYGOSCHOLA3 <- paste( V1, V2 , sep='|' )
SD_05_PC_CYMYGOSCHOLA3 <- xml_text( xml_find_all( doc, CYMYGOSCHOLA3 ) )





## VARIABLE NAME:  SD_05_PC_CYMYIEOLOSSE3
## DESCRIPTION:  Investment earnings or losses
## LOCATION:  SCHED-D-PART-05-LINE-1c
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus3Years/InvestmentEarningsOrLosses'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus3YrEndwmtFundGrp/InvestmentEarningsOrLossesAmt'
CYMYIEOLOSSE3 <- paste( V1, V2 , sep='|' )
SD_05_PC_CYMYIEOLOSSE3 <- xml_text( xml_find_all( doc, CYMYIEOLOSSE3 ) )





## VARIABLE NAME:  SD_05_PC_CUYEMIYEOTEX3
## DESCRIPTION:  Other expenditures
## LOCATION:  SCHED-D-PART-05-LINE-1e
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus3Years/OtherExpenditures'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus3YrEndwmtFundGrp/OtherExpendituresAmt'
CUYEMIYEOTEX3 <- paste( V1, V2 , sep='|' )
SD_05_PC_CUYEMIYEOTEX3 <- xml_text( xml_find_all( doc, CUYEMIYEOTEX3 ) )





## VARIABLE NAME:  SD_05_PC_CUYEMIYEADEX4
## DESCRIPTION:  Administrative expenses
## LOCATION:  SCHED-D-PART-05-LINE-1f
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus4Years/AdministrativeExpenses'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus4YrEndwmtFundGrp/AdministrativeExpensesAmt'
CUYEMIYEADEX4 <- paste( V1, V2 , sep='|' )
SD_05_PC_CUYEMIYEADEX4 <- xml_text( xml_find_all( doc, CUYEMIYEADEX4 ) )





## VARIABLE NAME:  SD_05_PC_CYMYBOYBALAN4
## DESCRIPTION:  Beginning of year balance
## LOCATION:  SCHED-D-PART-05-LINE-1a
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus4Years/BeginningOfYearBalance'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus4YrEndwmtFundGrp/BeginningYearBalanceAmt'
CYMYBOYBALAN4 <- paste( V1, V2 , sep='|' )
SD_05_PC_CYMYBOYBALAN4 <- xml_text( xml_find_all( doc, CYMYBOYBALAN4 ) )





## VARIABLE NAME:  SD_05_PC_CUYEMIYECOON4
## DESCRIPTION:  Current Year Minus4 Years - Contributions
## LOCATION:  SCHED-D-PART-05-LINE-1b
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus4Years/Contributions'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus4YrEndwmtFundGrp/ContributionsAmt'
CUYEMIYECOON4 <- paste( V1, V2 , sep='|' )
SD_05_PC_CUYEMIYECOON4 <- xml_text( xml_find_all( doc, CUYEMIYECOON4 ) )





## VARIABLE NAME:  SD_05_PC_CYMYEOYBALAN4
## DESCRIPTION:  End of year balance
## LOCATION:  SCHED-D-PART-05-LINE-1g
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus4Years/EndOfYearBalance'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus4YrEndwmtFundGrp/EndYearBalanceAmt'
CYMYEOYBALAN4 <- paste( V1, V2 , sep='|' )
SD_05_PC_CYMYEOYBALAN4 <- xml_text( xml_find_all( doc, CYMYEOYBALAN4 ) )





## VARIABLE NAME:  SD_05_PC_CYMYGOSCHOLA4
## DESCRIPTION:  Grants or scholarships
## LOCATION:  SCHED-D-PART-05-LINE-1d
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus4Years/GrantsOrScholarships'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus4YrEndwmtFundGrp/GrantsOrScholarshipsAmt'
CYMYGOSCHOLA4 <- paste( V1, V2 , sep='|' )
SD_05_PC_CYMYGOSCHOLA4 <- xml_text( xml_find_all( doc, CYMYGOSCHOLA4 ) )





## VARIABLE NAME:  SD_05_PC_CYMYIEOLOSSE4
## DESCRIPTION:  Investment earnings or losses
## LOCATION:  SCHED-D-PART-05-LINE-1c
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus4Years/InvestmentEarningsOrLosses'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus4YrEndwmtFundGrp/InvestmentEarningsOrLossesAmt'
CYMYIEOLOSSE4 <- paste( V1, V2 , sep='|' )
SD_05_PC_CYMYIEOLOSSE4 <- xml_text( xml_find_all( doc, CYMYIEOLOSSE4 ) )





## VARIABLE NAME:  SD_05_PC_CUYEMIYEOTEX4
## DESCRIPTION:  Other expenditures
## LOCATION:  SCHED-D-PART-05-LINE-1e
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/CurrentYearMinus4Years/OtherExpenditures'
V2 <- '//Return/ReturnData/IRS990ScheduleD/CYMinus4YrEndwmtFundGrp/OtherExpendituresAmt'
CUYEMIYEOTEX4 <- paste( V1, V2 , sep='|' )
SD_05_PC_CUYEMIYEOTEX4 <- xml_text( xml_find_all( doc, CUYEMIYEOTEX4 ) )





## VARIABLE NAME:  SD_05_PC_ENHEBYREORRG
## DESCRIPTION:  Endowments held by related organizations?
## LOCATION:  SCHED-D-PART-05-LINE-3a
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  checkbox

V1 <- '//Return/ReturnData/IRS990ScheduleD/EndowmentsHeldByRelatedOrgs'
V2 <- '//Return/ReturnData/IRS990ScheduleD/EndowmentsHeldRelatedOrgInd'
V3 <- '//Return/ReturnData/IRS990ScheduleD/Form990ScheduleDPartV/EndowmentsHeldByRelatedOrgs'
ENHEBYREORRG <- paste( V1, V2, V3 , sep='|' )
SD_05_PC_ENHEBYREORRG <- xml_text( xml_find_all( doc, ENHEBYREORRG ) )





## VARIABLE NAME:  SD_05_PC_ENHEBYUNORRG
## DESCRIPTION:  Endowments held by unrelated organizations?
## LOCATION:  SCHED-D-PART-05-LINE-3a
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  checkbox

V1 <- '//Return/ReturnData/IRS990ScheduleD/EndowmentsHeldByUnrelatedOrgs'
V2 <- '//Return/ReturnData/IRS990ScheduleD/EndowmentsHeldUnrelatedOrgInd'
V3 <- '//Return/ReturnData/IRS990ScheduleD/Form990ScheduleDPartV/EndowmentsHeldByUnrelatedOrgs'
ENHEBYUNORRG <- paste( V1, V2, V3 , sep='|' )
SD_05_PC_ENHEBYUNORRG <- xml_text( xml_find_all( doc, ENHEBYUNORRG ) )





## VARIABLE NAME:  SD_05_PC_PEENEOOYYBBA
## DESCRIPTION:  Permanent endowment EOY balance
## LOCATION:  SCHED-D-PART-05-LINE-2b
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/Form990ScheduleDPartV/PermanentEndowmentEOYBalance'
V2 <- '//Return/ReturnData/IRS990ScheduleD/PermanentEndowmentEOYBalance'
V3 <- '//Return/ReturnData/IRS990ScheduleD/PrmnntEndowmentBalanceEOYPct'
PEENEOOYYBBA <- paste( V1, V2, V3 , sep='|' )
SD_05_PC_PEENEOOYYBBA <- xml_text( xml_find_all( doc, PEENEOOYYBBA ) )





## VARIABLE NAME:  SD_05_PC_TEENEOOYYBBA
## DESCRIPTION:  Term endowment EOY balance
## LOCATION:  SCHED-D-PART-05-LINE-2c
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

V1 <- '//Return/ReturnData/IRS990ScheduleD/Form990ScheduleDPartV/TermEndowmentEOYBalance'
V2 <- '//Return/ReturnData/IRS990ScheduleD/TermEndowmentEOYBalance'
TEENEOOYYBBA <- paste( V1, V2 , sep='|' )
SD_05_PC_TEENEOOYYBBA <- xml_text( xml_find_all( doc, TEENEOOYYBBA ) )





## VARIABLE NAME:  SD_05_PC_TEBEOYPCT
## DESCRIPTION:  Term endowment EOY balance
## LOCATION:  SCHED-D-PART-05-LINE-2c
## TABLE:  SD-P05-T00-ENDOWMENT
## VARIABLE TYPE:  numeric

SD_05_PC_TEBEOYPCT <- xml_text( xml_find_all( doc, '/Return/ReturnData/IRS990ScheduleD/TermEndowmentBalanceEOYPct' ) )





namedList <- function(...){
      names <- as.list(substitute(list(...)))[-1L]
      result <- list(...)
      names(result) <- names
      result[sapply(result, function(x){length(x)==0})] <- NA
      result[sapply(result, is.null)] <- NA
      result
  }

d <- namedList( NAME, EIN, TAXYR, FORMTYPE, OBJECTID, URL, SD_05_PC_ARREORLISCR, SD_05_PC_BDBEOYPCT, SD_05_PC_CURYEAADMEXP, SD_05_PC_CUYEBEOFYEBA, SD_05_PC_CURRYEARCONT, SD_05_PC_CUYEENOFYEBA, SD_05_PC_CUYEGRORSCCH, SD_05_PC_CUYEINEAORLO, SD_05_PC_CURYEAOTHEXP, SD_05_PC_CUYEMIYEADEX1, SD_05_PC_CYMYBOYBALAN1, SD_05_PC_CUYEMIYECOON1, SD_05_PC_CYMYEOYBALAN1, SD_05_PC_CYMYGOSCHOLA1, SD_05_PC_CYMYIEOLOSSE1, SD_05_PC_CUYEMIYEOTEX1, SD_05_PC_CUYEMIYEADEX2, SD_05_PC_CYMYBOYBALAN2, SD_05_PC_CUYEMIYECOON2, SD_05_PC_CYMYEOYBALAN2, SD_05_PC_CYMYGOSCHOLA2, SD_05_PC_CYMYIEOLOSSE2, SD_05_PC_CUYEMIYEOTEX2, SD_05_PC_CUYEMIYEADEX3, SD_05_PC_CYMYBOYBALAN3, SD_05_PC_CUYEMIYECOON3, SD_05_PC_CYMYEOYBALAN3, SD_05_PC_CYMYGOSCHOLA3, SD_05_PC_CYMYIEOLOSSE3, SD_05_PC_CUYEMIYEOTEX3, SD_05_PC_CUYEMIYEADEX4, SD_05_PC_CYMYBOYBALAN4, SD_05_PC_CUYEMIYECOON4, SD_05_PC_CYMYEOYBALAN4, SD_05_PC_CYMYGOSCHOLA4, SD_05_PC_CYMYIEOLOSSE4, SD_05_PC_CUYEMIYEOTEX4, SD_05_PC_ENHEBYREORRG, SD_05_PC_ENHEBYUNORRG, SD_05_PC_PEENEOOYYBBA, SD_05_PC_TEENEOOYYBBA, SD_05_PC_TEBEOYPCT )

return( d )


}
```




## Helper Functions

```{r}
get_object_id <- function( url )
{
    object.id <- gsub( "https://s3.amazonaws.com/irs-form-990/", "", url )
    object.id <- gsub( "_public.xml", "", object.id )
    return( object.id )
}
```



# Test Build Function


```{r}
# i grabbed a couple that i know have data
V1 <- "https://s3.amazonaws.com/irs-form-990/201700619349300840_public.xml"
V2 <- "https://s3.amazonaws.com/irs-form-990/201710539349301106_public.xml"

doc <- read_xml( V1 ) %>% xml_ns_strip()
buildFUNCTION( doc, url=V1 )

doc <- read_xml( V2 ) %>% xml_ns_strip()
buildFUNCTION( doc, url=V2 )
```



# Put it in a Loop

We know these are Sched D filers already:

```{r, echo=T}
orgs <- 
c(
"https://s3.amazonaws.com/irs-form-990/201700619349300840_public.xml",
"https://s3.amazonaws.com/irs-form-990/201710539349301106_public.xml",
"https://s3.amazonaws.com/irs-form-990/201710889349301316_public.xml",
"https://s3.amazonaws.com/irs-form-990/201710869349300111_public.xml",
"https://s3.amazonaws.com/irs-form-990/201730459349301343_public.xml",
"https://s3.amazonaws.com/irs-form-990/201700589349300410_public.xml"
)
```


```{r}
buildSchedDPartV <- function( urls )
{
  
  library( dplyr )
  library( xml2 ) 
  
  # List of URLS to scrape
  
  these <- urls
  
  sd.part.v <- NULL
  
  for( i in 1:length(these) )
  {
     url.i <- these[i]
     doc.i <- read_xml( url.i ) %>% xml_ns_strip()
     
     num.nodes <- doc.i %>% xml_find_all( '//Return/ReturnData/IRS990ScheduleD/*' ) %>% length()
     if( num.nodes > 0 )
     {
       one.npo <- buildFUNCTION( doc=doc.i, url=url.i )
       sd.part.v <- bind_rows( sd.part.v, one.npo )
     }

  }
  
  return( as.data.frame( sd.part.v ) )

}
```


```{r}
dat.sd.p5 <- buildSchedDPartV( orgs )
```




## Try larger sample

Most are not Sched D filers. Return dataset will be small. 

Note the SCHEDD logical flag on the EFILE CORE is incorrect, but some of these will still work.


```{r, eval=F}
# 2016 EFILE CORE
dat <- readRDS( gzcon( url( "https://www.dropbox.com/s/4ptsnryf64vkqlg/2016-EFILE-CORE.rds?dl=1" ) ) )
d.sched.d <- dat[ dat$SCHEDD , ]
orgs <- head( d.sched.d$URL, 1000 )
```

Note run:

```{r, eval=F}
dat.sd.p5 <- buildSchedDPartV( orgs )
```

I added this line to check whether they have any SCHED D fields in their return, otherwise skip:

```{r, eval=F}
num.nodes <- doc.i %>% xml_find_all( '//Return/ReturnData/IRS990ScheduleD/*' ) %>% length()
if( num.nodes > 0 )
{
 one.npo <- buildFUNCTION( doc=doc.i, url=url.i )
 sd.part.v <- bind_rows( sd.part.v, one.npo )
}
```




# Build Full Dataset

Example code - I have not tested it! 

```{r, eval=F}
library( xmltools )
library( purrr )
library( xml2 )
library( dplyr )

source( "source_me.R" )

index <- buildIndex()

dir.create( "BUILD" )
setwd( "./BUILD" )




### BUILD ONE YEAR
# split full year into 1000 parts

buildYear <- function ( year, index=NULL )
{

	if( is.null(index) ){ index <- buildIndex() }

	dir.create( as.character(year) )
	setwd( paste( "./", year, sep="" ) )

	# create list of failed xml doc urls
	write.table( index[NULL,], file="FAIL_LIST.csv", sep=",", append=F, col.names=T, row.names=F ) 
	
	
	dd <- index[ index$TaxYear == year & index$FormType %in% c("990","990EZ") , ]

	nrow( dd )  

	# build in 100 small increments and save to file

	num.breaks <- round( (nrow(dd)/1000), 0 )

	breaks <- round( seq( from = 0, to = nrow(dd), length.out = num.breaks ), 0 )

	file.name <- paste( year, "-build.txt", sep="" )
	zz <- file( file.name, open = "wt" )
	sink( zz, split=T )
	sink( zz, type = "message", append=TRUE )
	
	print( paste( "There are", length(breaks), "loops." ) )

	redo.these <- 1:num.breaks
	
	df.list <- NULL

	for( i in 1:num.breaks )
	{
	   loop <- formatC( i, width = 3, format = "d", flag = "0" )
	   print( paste( "Loop-", loop, ": ", format(Sys.time(), "%b %d %X"), sep="" ) )
	   d.sub <- dd[ (breaks[i]+1):( breaks[i+1] ) , ]

	   try( {

		    df.list[[i]] <- buildSchedDPartV( d.sub$URL )
		    redo.these[i] <- NA

	   } )



	}

  df <- bind_rows( df.list )
  
  time <- format(Sys.time(), "%b-%d-%Y-%Hh-%Mm")
  saveRDS( df, paste0( year, "-SCHED-D-PART-V ", time, ".rds" ) )
  write.csv( df, paste0( year, "-SCHED-D-PART-V ", time, ".csv" ) )
  
	redo.these

	sink(type = "message")

	sink() # close sink
	close(zz)
	file.show( file.name )

	savehistory( file=paste( year, "-build.Rhistory", sep="" ) )
	
	return( df )

}
```

```{r, eval=F}
dat.sd.p5.2009 <- buildYear( year=2009, index=index )
setwd( ".." )
getwd()  # should be back to BUILD
```


