---
title: "Schedule C RDB 1:M Examples"
date: "March 2022"
output:
  html_document:
    theme: readable
    df_print: paged
    highlight: tango
    smart: false
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set( echo=TRUE, message=F, warning=F )
```


# Packages

```{r}
# package.list <- c( "xmltools","purrr","xml2","dplyr","pander","XML" )
# install.packages( package.list  )

library( xmltools )      # xml tools
library( xml2 )          # xml tools 
library( XML )           # xml tools

library( dplyr )         # data wrangling 
library( purrr )         # data wrangling 

library( pander )        # pretty tables 
library( DiagrammeR )    # network diagrams 
```



# Demo Table Extraction Functions


Demo XML data from Part V of Schedule H - the table of facilities. 


```{r}
sierraclub<- 
"<SIERRACLUB>
<Section527PoliticalOrgGrp>
        <OrganizationBusinessName>
          <BusinessNameLine1Txt>THE SIERRA CLUB VOTER EDUCATION FUND</BusinessNameLine1Txt>
        </OrganizationBusinessName>
        <USAddress>
          <AddressLine1Txt>2101 WEBSTER STREET SUITE 1300</AddressLine1Txt>
          <CityNm>OAKLAND</CityNm>
          <StateAbbreviationCd>CA</StateAbbreviationCd>
          <ZIPCd>94612</ZIPCd>
        </USAddress>
        <EIN>943244759</EIN>
        <ContributionsRcvdDlvrAmt>241025</ContributionsRcvdDlvrAmt>
      </Section527PoliticalOrgGrp>
      </SIERRACLUB>"
```



```{r}
doc <- xml2::read_xml( sierraclub )
nodeset <- xml2::xml_children( doc ) # top level nodeset
xmltools::xml_view_trees( doc )
```



## Convert nodeset to Data Frames

```{r}
doc <- xml2::read_xml(sierraclub)

# nodeset is a group of nodes returned
# from the previous step
nodeset_to_df <- function( nodeset )
{
  node_to_df <- function(x)
  { 
    vec <- xml_text(xml_children(x))
    names(vec) <- xml_name(xml_children(x)) 
    df <- data.frame( as.list( vec ), stringsAsFactors=F )
    return( df )
  }
  
  node.list <- lapply( nodeset, node_to_df )
  df <- bind_rows( node.list )
  return( df )
}

# xml2::xml_structure( doc )
# nodeset <- xml2::xml_children( doc )
# nodeset_to_df( nodeset )

group.name.1 <- "//Section527PoliticalOrgGrp"
group.name.2 <- "//Sec527PolOrgs"
group.name.3 <- "//Form990ScheduleCPartI/Sec527PolOrgs"


all.versions <- paste( group.name.1, group.name.2,group.name.3, sep="|" )

# sierra club
V1 <- "https://s3.amazonaws.com/irs-form-990/201843129349301954_public.xml"
doc <- read_xml( V1 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
nodeset_to_df( node.group ) %>% pander()
```




# Load Concordance File


```{r}
# load concordance for schedule h
#dropbox.url <- "https://www.dropbox.com/s/k2tohl0ik4odjii/schedule-h-v1.csv?dl=1"

dropbox <- "https://www.dropbox.com/s/z00h5n2eimjhuyl/schedule-c.csv?dl=1"
sched.c <- read.csv( file=dropbox )
head( sched.c ) %>% pander()
```


```{r}
# remove leading forward slash
# though we need to add it back below
xpaths <- sched.c$xpath 
xpaths <- gsub( "/Return/", "Return/", xpaths )
```


## Get xpaths for Each RDB Table

SC-P01-T00-LOBBY

* IRS 990 Schedule C 
* Part 01 on the 990 form 
* Table-00 (all zeros are one-to-one tables)
* Topic = lobbying 

SC-P01-T01-POLITICAL-ORGS-INFO

* Table-01 and above are one-to-many tables 

```{r}
table( sched.c$rdb_table )
```


Get xpaths for the one-to-many tables: 

```{r}
xpaths.t1 <- xpaths[ sched.c$rdb_table == "SC-P01-T01-POLITICAL-ORGS-INFO" ]
xpaths.t2 <- xpaths[ sched.c$rdb_table == "SC-P04-T99-SUPPLEMENTAL-INFO" ]
```



## Compare xpath Levels

```{r}
nodes <- strsplit( xpaths.t1, "/" )

xpath.levels <- sapply( nodes, length )
max.lev <- max( xpath.levels )
nodes <- lapply( nodes, function(x){ c(x, rep("",max.lev-length(x) ) ) } )

# compare xpath levels
xpath.levels <- data.frame( do.call( cbind, nodes ), stringsAsFactors=F )
xpath.levels[ , 1:10 ]%>% pander
```


# Identify Group Levels


## Find Grouping Variables

This one works well but only works on active xpaths in a specific XML document. We can't use it with the list of raw xpaths from the concordance file.

```{r}
## we can identify grouping variables
doc <- xml2::read_xml( sierraclub )

## get all xpaths
all.xpaths <- doc %>% 
  xml_get_paths()

## collapse xpaths to unique only
unique.xpaths <- all.xpaths %>%
  unlist() %>%
  unique()

## but what we really want is the parent node of terminal nodes.
## use the `only_terminal_parent = TRUE` to do this

## get all xpaths to parents of parent node
groups.all <- doc %>% 
  xml_get_paths( only_terminal_parent = TRUE )

## collapse xpaths to unique only
groups <- groups.all %>% 
  unlist() %>%
  unique()

groups
```


This will return all variables at the first level where the nodes split. Some will be grouping variables, and some will be regular variables. Have to inspect to see. 

*I need to improve this to return only grouping variables, if possible.*

```{r}
find_group_name <- function( xpaths )
{
  nodes <- strsplit( xpaths, "/" )
  d1 <- data.frame( do.call( cbind, nodes ), stringsAsFactors=F )
  not.equal <- apply( d1, MARGIN=1, FUN=function(x){ length( unique( x )) > 1 } ) 
  this.one <- which( not.equal == T )[ 1 ]
  group.names <- d1[ this.one,  ] %>% as.character() %>% unique()
  return( group.names )
}

find_group_name( xpaths.t1 ) 
find_group_name( xpaths.t2 ) 

```



## Sample data from Schedule C Part I-C Line 5 and part IV

```{r}
# node groups for Schedule C Part I-C Line 5
group.name.1 <- "//Section527PoliticalOrgGrp"
group.name.2 <- "//Sec527PolOrgs"
group.name.3 <- "//Form990ScheduleCPartI/Sec527PolOrgs"
all.versions <- paste( group.name.1, group.name.2,group.name.3, sep="|" )

# node groups for Schedule C Part IV
group.name.4 <- "//Form990ScheduleCPartIV"
group.name.5 <- "//SupplementalInformationDetail"
all.versions2 <- paste( group.name.4, group.name.5, sep="|" )


# sierra club 
V1 <- "https://s3.amazonaws.com/irs-form-990/201843129349301954_public.xml"

# SOUTHERN POVERTY LAW CENTER INC , do not have data in part I-C
V2 <- "https://s3.amazonaws.com/irs-form-990/201900309349301030_public.xml"

#AMERICAN CIVIL LIBERTIES UNION FOUNDATION INC, do not have data in part I-C
V3 <- "https://s3.amazonaws.com/irs-form-990/201842749349301309_public.xml"

#National Association for the Advancement of Colored People, do not have data in part I-C
V4 <- "https://s3.amazonaws.com/irs-form-990/201813189349309906_public.xml"

#PLANNED PARENTHOOD GLOBAL INC

V5 <- "https://s3.amazonaws.com/irs-form-990/201821359349309027_public.xml"

#for table-01
list.of.tables <- list()

doc <- read_xml( V1 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[1]] <- nodeset_to_df( node.group )

doc <- read_xml( V2 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[2]] <- nodeset_to_df( node.group )

doc <- read_xml( V3 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[3]] <- nodeset_to_df( node.group )

doc <- read_xml( V4 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[4]] <- nodeset_to_df( node.group )

doc <- read_xml( V5 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[5]] <- nodeset_to_df( node.group )

# list.of.tables

bind_rows( list.of.tables ) 
payment_political_orgs <-bind_rows( list.of.tables ) 


```

## Sample data from Schedule C Part IV


```{r}
############# for table 02

list.of.tables2 <- list()

doc <- read_xml( V1 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions2 )
list.of.tables2[[1]] <- nodeset_to_df( node.group )

doc <- read_xml( V2 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions2 )
list.of.tables2[[2]] <- nodeset_to_df( node.group )

doc <- read_xml( V3 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions2 )
list.of.tables2[[3]] <- nodeset_to_df( node.group )

doc <- read_xml( V4 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions2 )
list.of.tables2[[4]] <- nodeset_to_df( node.group )

doc <- read_xml( V5 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions2 )
list.of.tables2[[5]] <- nodeset_to_df( node.group )

# list.of.tables

bind_rows( list.of.tables2 ) 
suplemental_info <- bind_rows( list.of.tables2 ) 


```


Once all of the group names are properly identified for each relational table we can construct the build functions for the relational databases. 

The will look something like this, where "hospitals" is the index file with all Schedule H returns from a year. 

<br>
<br>



```{r, eval=F}
# hypoethetical build file

#group.name.1 <- "//Section527PoliticalOrgGrp"
#group.name.2 <- "//Sec527PolOrgs"
#group.name.3 <- "//Form990ScheduleCPartI/Sec527PolOrgs"
#all.versions <- paste( group.name.1, group.name.2,group.name.3, sep="|" )

# node groups for Schedule C Part IV
#group.name.4 <- "//Form990ScheduleCPartIV"
#group.name.5 <- "//SupplementalInformationDetail"
#all.versions2 <- paste( group.name.4, group.name.5, sep="|" )


#i.counter <- 1

#sched.h.part.v <- list()

#for( i in hospitals$URL )
#{
  #doc <- read_xml( i ) %>% xml_ns_strip()
  #node.group <- xml_find_all( doc, all.versions )
  #sched.h.part.v [[ i.counter ]] <- nodeset_to_df( node.group )
  
  #i.counter <- i.counter + 1
#}
```


<br>
<br>
<br>

-------------------

<br>
<br>
<br>

<br>
<br>
<br>



## Find More Hospital Data From EFILE CORE

```{r, eval=F}
# load 2016 EFILE CORE
dat <- readRDS( gzcon( url( "https://www.dropbox.com/s/4ptsnryf64vkqlg/2016-EFILE-CORE.rds.rds?dl=1" ) ) )
head(dat) %>% pander()

# find schedule C filers

dat.c <- dplyr::filter( dat, SCHEDC=="TRUE" )

political_orgs<- head( dat.c$URL )

```


<br>
<br>
<br>


---------------------------  


<br>
<br>
<br>






# Explore XML Formats



## Flatten Groups to Tables

From the XML package - our doc is an xml2 object so not compatible.

```{r}
doc <- XML::xmlParse( sierraclub )
nodes <- XML::getNodeSet( doc, "//SIERRACLUB/Section527PoliticalOrgGrp" )
XML::xmlToDataFrame( doc )
XML::xmlToDataFrame( nodes )

# this doesn't work - puts all in one row
# XML::xmlToList( doc ) %>% as.data.frame( stringsAsFactors=F )

# works for one node set
# XML::xmlToList( nodes[[1]] ) %>% as.data.frame( stringsAsFactors=F )
```




## Print Document Structure

Various options in various packages:

```{r}
doc <- xml2::read_xml( sierraclub )
nodeset <- xml2::xml_children( doc ) # top level nodeset
xml2::xml_structure( doc )
```

```{r}
xmltools::xml_get_paths( doc )
xmltools::xml_view_trees( doc )
xmltools::xml_get_paths( doc, mark_terminal = "--->  " )
```




## Visualizing Variable Hierarchy

```{r}
for( i in 1:max.lev )
{
  row.i <- as.character(xpath.levels[i,])
  print( paste0( "LEVEL ", i, ": " ) )
  print( paste0( sort(unique( row.i )), collapse="; " ) )
  cat( "\n" )
}
```



```{r}
create_edgelist <- function( xpaths )
{
  nodes <- strsplit( xpaths, "/" )
  xpath.levels <- sapply( nodes, length )
  max.lev <- max( xpath.levels )
  nodes <- lapply( nodes, function(x){ c(x, rep("",max.lev-length(x) ) ) } )
  xpath.levels <- data.frame( do.call( cbind, nodes ), stringsAsFactors=F )
  
  df <- NULL
  
  for( i in 1:ncol(xpath.levels) )
  {
    for( j in 1:(max.lev-1) )
    {
      df <- rbind( df, xpath.levels[ j:(j+1), i ] )
    }
  }
  
  df <- as.data.frame(df, stringsAsFactors=F )
  df <- unique( df )
  df <- df[ ! grepl( "$^", df$V2 ) , ]
  
  return( df )
}

el <- create_edgelist( xpaths.t2 )


doc <- xml2::read_xml( sierraclub )
nodeset <- xml2::xml_children( doc ) # top level nodeset
xpaths.sierraclub<- xmltools::xml_get_paths( doc ) %>% unlist() %>% unique()
xpaths.sierraclub <- gsub( "/SIERRACLUB/", "SIERRACLUB/", xpaths.sierraclub )
el <- create_edgelist( xpaths.sierraclub )
```




```{r, fig.height=8, fig.width=8}
library( igraph )
g <- graph_from_data_frame( d=el, directed=TRUE, vertices=NULL )
plot( g, layout=layout_as_tree )

```







```{r}
library( data.tree )
nd <- FromDataFrameNetwork( network=el )
print( nd )
```


```{r, fig.width=10}
SetGraphStyle( nd, rankdir = "TB")
SetEdgeStyle( nd, arrowhead = "vee", color = "grey20", penwidth = 2 )
SetNodeStyle( nd, 
              style = "filled,rounded", 
              shape = "box", 
              fillcolor = "LightBlue", 
              fontname = "helvetica", 
              fontcolor="black",
              tooltip = GetDefaultTooltip )

# SetNodeStyle(acme$IT, fillcolor = "LightBlue", penwidth = "5px")
plot( nd )
```


```{r, fig.width=10}
library(networkD3)
net <- ToDataFrameNetwork( nd, "name" )
simpleNetwork( net[-3], fontSize = 12 )
```


```{r}
el <- create_edgelist( xpaths.t1 )
nd <- FromDataFrameNetwork( network=el )
net <- ToDataFrameNetwork( nd, "name" )
simpleNetwork( el, fontSize = 12 , linkDistance = 25, charge = -100 )
```

