---
title: "schedule-h-rdb-table.rmd"
author: "Qingqing"
date: "2019/6/26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library( xmltools )
library( purrr )
library( xml2 )
library( XML )
library( dplyr )
library( pander )
```


```{r}
reading <-
"<READING>   
      <OthHlthCareFcltsNotHospitalGrp>
        <OthHlthCareFcltsGrp>
          <BusinessName>
            <BusinessNameLine1Txt>TRHMC SURGICENTER AT SPRING RIDGE</BusinessNameLine1Txt>
          </BusinessName>
          <USAddress>
            <AddressLine1Txt>2603 KEISER BLVD</AddressLine1Txt>
            <CityNm>READING</CityNm>
            <StateAbbreviationCd>PA</StateAbbreviationCd>
            <ZIPCd>19610</ZIPCd>
          </USAddress>
          <FacilityTxt>AMBULATORY SURGERY CENTER</FacilityTxt>
        </OthHlthCareFcltsGrp>
      </OthHlthCareFcltsNotHospitalGrp>
</READING>"

```

```{r}

doc <- xml2::read_xml( reading)
nodeset <- xml2::xml_children( doc ) # top level nodeset
xmltools::xml_view_trees( doc )
```

```{r}

doc <- xml2::read_xml( reading )

# nodeset is a group of nodes returned
# from the previous step
nodeset_to_df <- function( nodeset )
{
  node_to_df <- function(x)
  { 
    vec <- xml_text(xml_children(x))
    names(vec) <- xml_name(xml_children(x)) 
    df <- data.frame( as.list( vec ), stringsAsFactors=F )
    return( df )
  }
  
  node.list <- lapply( nodeset, node_to_df )
  df <- bind_rows( node.list )
  return( df )
}

# xml2::xml_structure( doc )
# nodeset <- xml2::xml_children( doc )
# nodeset_to_df( nodeset )

group.name.5 <- "//OthHlthCareFcltsNotHospitalGrp/OthHlthCareFcltsGrp"
group.name.6 <- "//Form990ScheduleHPartVSectionC/OtherFacilities"
all.versions <- paste( group.name.5, group.name.6, sep="|" )

# reading hospital
O1 <- "https://s3.amazonaws.com/irs-form-990/201821039349300712_public.xml"
doc <- read_xml( O1 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
nodeset_to_df( node.group ) %>% pander()


```
# Load Concordance File


```{r}
# load concordance for schedule h
dropbox.url <- "https://www.dropbox.com/s/k2tohl0ik4odjii/schedule-h-v1.csv?dl=1"
sh <- read.csv( dropbox.url, stringsAsFactors=F )

# remove leading forward slash
# though we need to add it back below
xpaths <- sh$xpath 
xpaths <- gsub( "/Return/", "Return/", xpaths )
```

## Get xpaths for Each RDB Table

```{r}
table( sh$rdb_table )

xpaths.t1 <- xpaths[ sh$rdb_table == "SH-TABLE-01-COMPANY-JOINT-VENTURES" ]
xpaths.t2 <- xpaths[ sh$rdb_table == "SH-TABLE-02-HOSPITAL-FACILITY" ]
xpaths.t3 <- xpaths[ sh$rdb_table == "SH-TABLE-03-OTHER-CARE-FACILITY" ]
xpaths.t4 <- xpaths[ sh$rdb_table == "SH-TABLE-04-SUPPL-INFO" ]
```



## Compare xpath Levels # imortant steps 

```{r}
nodes <- strsplit( xpaths.t3, "/" )

xpath.levels <- sapply( nodes, length )
max.lev <- max( xpath.levels )
nodes <- lapply( nodes, function(x){ c(x, rep("",max.lev-length(x) ) ) } )

# compare xpath levels
xpath.levels <- data.frame( do.call( cbind, nodes ), stringsAsFactors=F )
xpath.levels[ , 1:10 ] %>% pander
```




# Identify Group Levels


## Find Grouping Variables

This one works well but only works on active xpaths in a specific XML document. We can't use it with the list of raw xpaths from the concordance file.

```{r}
## we can identify grouping variables
doc <- xml2::read_xml( reading )

## get all xpaths
all.xpaths <- doc %>% 
  xml_get_paths()

## collapse xpaths to unique only
unique.xpaths <- all.xpaths %>%
  unlist() %>%
  unique()

## but what we really want is the parent node of terminal nodes.
## use the `only_terminal_parent = TRUE` to do this

## get all xpaths to parents of parent node
groups.all <- doc %>% 
  xml_get_paths( only_terminal_parent = TRUE )

## collapse xpaths to unique only
groups <- groups.all %>% 
  unlist() %>%
  unique()

groups
```

This will return all variables at the first level where the nodes split. Some will be grouping variables, and some will be regular variables. Have to inspect to see. 

*I need to improve this to return only grouping variables, if possible.*

```{r}
find_group_name <- function( xpaths )
{
  nodes <- strsplit( xpaths, "/" )
  d1 <- data.frame( do.call( cbind, nodes ), stringsAsFactors=F )
  not.equal <- apply( d1, MARGIN=1, FUN=function(x){ length( unique( x )) > 1 } ) 
  this.one <- which( not.equal == T )[ 1 ]
  group.names <- d1[ this.one,  ] %>% as.character() %>% unique()
  return( group.names )
}

find_group_name( xpaths.t3 ) 
```



## Sample data from Schedule H Part IV 
```{r}

group.name.5 <- "//OthHlthCareFcltsNotHospitalGrp/OthHlthCareFcltsGrp"
group.name.6 <- "//Form990ScheduleHPartVSectionC/OtherFacilities"
all.versions <- paste( group.name.5, group.name.6, sep="|" )

#READING HOSPITAL# skip column d #1 entity
M1 <- "https://s3.amazonaws.com/irs-form-990/201821039349300712_public.xml"

#ABINGTON MEMORIAL HOSPITAL# skip column d # 47 entities
M2 <-  "https://s3.amazonaws.com/irs-form-990/201831359349306048_public.xml"

#LEHIGH VALLEY HOSPITAL # 0 entity
M3 <- "https://s3.amazonaws.com/irs-form-990/201801319349300130_public.xml"


#Charlotte Hungerford Hospital# skip column d # 13 entities
M4 <- "https://s3.amazonaws.com/irs-form-990/201802259349302005_public.xml"


# BRIDGEPORT HOSPITAL ,25 entities
M5 <- "https://s3.amazonaws.com/irs-form-990/201832259349301448_public.xml"


# GRADY MEMORIAL HOSPITAL CORPORATION , 10 entities
M6 <- "https://s3.amazonaws.com/irs-form-990/201813189349303776_public.xml"




```


```{r}

list.of.tables <- list()

doc <- read_xml( M1 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[1]] <- nodeset_to_df( node.group )


doc <- read_xml( M2 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[2]] <- nodeset_to_df( node.group )

doc <- read_xml( M3 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[3]] <- nodeset_to_df( node.group )

doc <- read_xml( M4 ) %>%  xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[4]] <- nodeset_to_df( node.group )

doc <- read_xml( M5 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[5]] <- nodeset_to_df( node.group )

doc <- read_xml( M6 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[6]] <- nodeset_to_df( node.group )

# list.of.tables # missing M6 

nonhospitalfacilty<- bind_rows( list.of.tables ) 


```







