---
title: "Schedule H"
date: "June 25, 2019"
output:
  html_document:
    theme: readable
    df_print: paged
    highlight: tango
    smart: false
    toc: yes
    toc_float: no
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set( echo=TRUE, message=F, warning=F, fig.width=10 )
```


```{css, echo=F}
h1, h2{
  margin-top:100px;
  margin-bottom:20px;
}

table
{ 
    margin-left: auto;
    margin-right: auto;
    margin-top:80px;
    margin-bottom:800px;
}

img {
    max-width: 90%;
    display: block;
    margin-right: auto;
    margin-left: auto;
    margin-top:30px;
    margin-bottom:20px;
}
```


# Packages

```{r}
# package.list <- c( "xmltools","purrr","xml2","dplyr","pander","XML" )
# install.packages( package.list  )

library( xmltools )
library( purrr )
library( xml2 )
library( XML )
library( dplyr )
library( pander )
```



# Demo Table Extraction Functions


Demo XML data from Part V of Schedule H - the table of facilities. 


```{r}
grady <- 
"<GRADY>
<HospitalFacilitiesGrp>
<FacilityNum>1</FacilityNum>
<BusinessName>
<BusinessNameLine1Txt>GRADY MEMORIAL HOSPITAL</BusinessNameLine1Txt>
</BusinessName>
<USAddress>
<AddressLine1Txt>80 JESSE HILL JR DRIVE SE</AddressLine1Txt>
<CityNm>ATLANTA</CityNm>
<StateAbbreviationCd>GA</StateAbbreviationCd>
<ZIPCd>30303</ZIPCd>
</USAddress>
<WebsiteAddressTxt>https://www.gradyhealth.org</WebsiteAddressTxt>
<LicensedHospitalInd>X</LicensedHospitalInd>
<GeneralMedicalAndSurgicalInd>X</GeneralMedicalAndSurgicalInd>
<TeachingHospitalInd>X</TeachingHospitalInd>
<ResearchFacilityInd>X</ResearchFacilityInd>
<EmergencyRoom24HrsInd>X</EmergencyRoom24HrsInd>
</HospitalFacilitiesGrp>
<HospitalFacilitiesGrp>
<FacilityNum>2</FacilityNum>
<BusinessName>
<BusinessNameLine1Txt>HUGHES SPALDING CHILDRENS HOSPITAL</BusinessNameLine1Txt>
</BusinessName>
<USAddress>
<AddressLine1Txt>45 JESSE HILL JR DRIVE SE</AddressLine1Txt>
<CityNm>ATLANTA</CityNm>
<StateAbbreviationCd>GA</StateAbbreviationCd>
<ZIPCd>30303</ZIPCd>
</USAddress>
<StateLicenseNum>https://www.gradyhealth.org</StateLicenseNum>
<ChildrensHospitalInd>X</ChildrensHospitalInd>
<TeachingHospitalInd>X</TeachingHospitalInd>
<EmergencyRoom24HrsInd>X</EmergencyRoom24HrsInd>
</HospitalFacilitiesGrp>
</GRADY>"
```



```{r}
doc <- xml2::read_xml( grady )
nodeset <- xml2::xml_children( doc ) # top level nodeset
xmltools::xml_view_trees( doc )
```



## Convert nodeset to Data Frames

```{r}
doc <- xml2::read_xml( grady )

# nodeset is a group of nodes returned
# from the previous step
nodeset_to_df <- function( nodeset )
{
  node_to_df <- function(x)
  { 
    vec <- xml_text(xml_children(x))
    names(vec) <- xml_name(xml_children(x)) 
    df <- data.frame( as.list( vec ), stringsAsFactors=F )
    return( df )
  }
  
  node.list <- lapply( nodeset, node_to_df )
  df <- bind_rows( node.list )
  return( df )
}

# xml2::xml_structure( doc )
# nodeset <- xml2::xml_children( doc )
# nodeset_to_df( nodeset )

# The more general version is below, uses all group versions:
# 
# group.name.1 <- "//Form990ScheduleHPartVSectionA"
# group.name.2 <- "//HospitalFacilitiesGrp"
# all.versions <- paste( group.name.1, group.name.2, sep="|" )
# node.group <- xml_find_all( doc, "//HospitalFacilitiesGrp" )
# nodeset_to_df( node.group )

# grady hospital
V1 <- "https://s3.amazonaws.com/irs-form-990/201813189349303776_public.xml"
doc <- read_xml( V1 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, "//HospitalFacilitiesGrp" )
nodeset_to_df( node.group ) %>% pander()
```







# Load Concordance File


```{r}
# load concordance for schedule h
dropbox.url <- "https://www.dropbox.com/s/k2tohl0ik4odjii/schedule-h-v1.csv?dl=1"
sh <- read.csv( dropbox.url, stringsAsFactors=F )

# remove leading forward slash
# though we need to add it back below
xpaths <- sh$xpath 
xpaths <- gsub( "/Return/", "Return/", xpaths )
```



## Get xpaths for Each RDB Table

```{r}
table( sh$rdb_table )

xpaths.t1 <- xpaths[ sh$rdb_table == "SH-TABLE-01-COMPANY-JOINT-VENTURES" ]
xpaths.t2 <- xpaths[ sh$rdb_table == "SH-TABLE-02-HOSPITAL-FACILITY" ]
xpaths.t3 <- xpaths[ sh$rdb_table == "SH-TABLE-03-OTHER-CARE-FACILITY" ]
xpaths.t4 <- xpaths[ sh$rdb_table == "SH-TABLE-04-SUPPL-INFO" ]
```






## Compare xpath Levels

```{r}
nodes <- strsplit( xpaths.t2, "/" )

xpath.levels <- sapply( nodes, length )
max.lev <- max( xpath.levels )
nodes <- lapply( nodes, function(x){ c(x, rep("",max.lev-length(x) ) ) } )

# compare xpath levels
xpath.levels <- data.frame( do.call( cbind, nodes ), stringsAsFactors=F )
xpath.levels[ , 1:10 ] %>% pander
```









# Identify Group Levels


## Find Grouping Variables

This one works well but only works on active xpaths in a specific XML document. We can't use it with the list of raw xpaths from the concordance file.

```{r}
## we can identify grouping variables
doc <- xml2::read_xml( grady )

## get all xpaths
all.xpaths <- doc %>% 
  xml_get_paths()

## collapse xpaths to unique only
unique.xpaths <- all.xpaths %>%
  unlist() %>%
  unique()

## but what we really want is the parent node of terminal nodes.
## use the `only_terminal_parent = TRUE` to do this

## get all xpaths to parents of parent node
groups.all <- doc %>% 
  xml_get_paths( only_terminal_parent = TRUE )

## collapse xpaths to unique only
groups <- groups.all %>% 
  unlist() %>%
  unique()

groups
```


This will return all variables at the first level where the nodes split. Some will be grouping variables, and some will be regular variables. Have to inspect to see. 

*I need to improve this to return only grouping variables, if possible.*

```{r}
find_group_name <- function( xpaths )
{
  nodes <- strsplit( xpaths, "/" )
  d1 <- data.frame( do.call( cbind, nodes ), stringsAsFactors=F )
  not.equal <- apply( d1, MARGIN=1, FUN=function(x){ length( unique( x )) > 1 } ) 
  this.one <- which( not.equal == T )[ 1 ]
  group.names <- d1[ this.one,  ] %>% as.character() %>% unique()
  return( group.names )
}

find_group_name( xpaths.t2 ) 
```






## Sample data from Schedule H Part V

```{r}
# node groups for Sched-H Part V
group.name.1 <- "//Form990ScheduleHPartVSectionA"
group.name.2 <- "//HospitalFacilitiesGrp"
all.versions <- paste( group.name.1, group.name.2, sep="|" )


# grady hospital
V1 <- "https://s3.amazonaws.com/irs-form-990/201813189349303776_public.xml"
# other hospitals?
V2 <- "https://s3.amazonaws.com/irs-form-990/201832259349301448_public.xml"
V3 <- "https://s3.amazonaws.com/irs-form-990/201841359349304794_public.xml"
V4 <- "https://s3.amazonaws.com/irs-form-990/201811949349301226_public.xml"
V5 <- "https://s3.amazonaws.com/irs-form-990/201801349349305480_public.xml"



list.of.tables <- list()

doc <- read_xml( V1 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[1]] <- nodeset_to_df( node.group )

doc <- read_xml( V2 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[2]] <- nodeset_to_df( node.group )

doc <- read_xml( V3 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[3]] <- nodeset_to_df( node.group )

doc <- read_xml( V4 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[4]] <- nodeset_to_df( node.group )

doc <- read_xml( V5 ) %>% xml_ns_strip()
node.group <- xml_find_all( doc, all.versions )
list.of.tables[[5]] <- nodeset_to_df( node.group )

# list.of.tables

bind_rows( list.of.tables ) 
```


Once all of the group names are properly identified for each relational table we can construct the build functions for the relational databases. 

The will look something like this, where "hospitals" is the index file with all Schedule H returns from a year. 

<br>
<br>



```{r, eval=F}
# hypoethetical build file

# node groups for Sched-H Part V
group.name.1 <- "//Form990ScheduleHPartVSectionA"
group.name.2 <- "//HospitalFacilitiesGrp"
all.versions <- paste( group.name.1, group.name.2, sep="|" )


i.counter <- 1

sched.h.part.v <- list()

for( i in hospitals$URL )
{
  doc <- read_xml( i ) %>% xml_ns_strip()
  node.group <- xml_find_all( doc, all.versions )
  sched.h.part.v [[ i.counter ]] <- nodeset_to_df( node.group )
  
  i.counter <- i.counter + 1
}
```


<br>
<br>
<br>

-------------------

<br>
<br>
<br>

<br>
<br>
<br>



## Find More Hospital Data From EFILE CORE

```{r, echo=F}
hospitals <- 
c("https://s3.amazonaws.com/irs-form-990/201700849349200100_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201720469349300742_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201700569349300015_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201720619349200117_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201720829349300702_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201700499349300305_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201730659349300323_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201720349349200332_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201740589349200034_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201720279349200612_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201710669349300526_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201740269349200414_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201700729349200615_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201730399349200518_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201700659349200765_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201700869349300725_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201710659349300716_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201730399349200103_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201710589349200106_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201720879349300862_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201710689349200301_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201710879349200216_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201740839349200129_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201721019349300912_public.xml", 
"https://s3.amazonaws.com/irs-form-990/201731469349200213_public.xml"
)
```


```{r, eval=F}
# load 2016 EFILE CORE
dat <- readRDS( gzcon( url( "https://www.dropbox.com/s/4ptsnryf64vkqlg/2016-EFILE-CORE.rds?dl=1" ) ) )

# find likely schedule H filers
dat.h <- dat[ grepl( "HOSPITAL", dat$NAME ) , ]
hospitals <- head( dat.h$URL )
 [1] "https://s3.amazonaws.com/irs-form-990/201700849349200100_public.xml"
 [2] "https://s3.amazonaws.com/irs-form-990/201720469349300742_public.xml"
 [3] "https://s3.amazonaws.com/irs-form-990/201700569349300015_public.xml"
 [4] "https://s3.amazonaws.com/irs-form-990/201720619349200117_public.xml"
 [5] "https://s3.amazonaws.com/irs-form-990/201720829349300702_public.xml"
 [6] "https://s3.amazonaws.com/irs-form-990/201700499349300305_public.xml"

```


<br>
<br>
<br>


---------------------------  


<br>
<br>
<br>






# Explore XML Formats



## Flatten Groups to Tables

From the XML package - our doc is an xml2 object so not compatible.

```{r}
doc <- XML::xmlParse( grady )
nodes <- XML::getNodeSet( doc, "//GRADY/HospitalFacilitiesGrp" )
XML::xmlToDataFrame( doc )
XML::xmlToDataFrame( nodes )

# this doesn't work - puts all in one row
# XML::xmlToList( doc ) %>% as.data.frame( stringsAsFactors=F )

# works for one node set
# XML::xmlToList( nodes[[1]] ) %>% as.data.frame( stringsAsFactors=F )
```




## Print Document Structure

Various options in various packages:

```{r}
doc <- xml2::read_xml( grady )
nodeset <- xml2::xml_children( doc ) # top level nodeset
xml2::xml_structure( doc )
```

```{r}
xmltools::xml_get_paths( doc )
xmltools::xml_view_trees( doc )
xmltools::xml_get_paths( doc, mark_terminal = "--->  " )
```




## Visualizing Variable Hierarchy

```{r}
for( i in 1:max.lev )
{
  row.i <- as.character(xpath.levels[i,])
  print( paste0( "LEVEL ", i, ": " ) )
  print( paste0( sort(unique( row.i )), collapse="; " ) )
  cat( "\n" )
}
```



```{r}
create_edgelist <- function( xpaths )
{
  nodes <- strsplit( xpaths, "/" )
  xpath.levels <- sapply( nodes, length )
  max.lev <- max( xpath.levels )
  nodes <- lapply( nodes, function(x){ c(x, rep("",max.lev-length(x) ) ) } )
  xpath.levels <- data.frame( do.call( cbind, nodes ), stringsAsFactors=F )
  
  df <- NULL
  
  for( i in 1:ncol(xpath.levels) )
  {
    for( j in 1:(max.lev-1) )
    {
      df <- rbind( df, xpath.levels[ j:(j+1), i ] )
    }
  }
  
  df <- as.data.frame(df, stringsAsFactors=F )
  df <- unique( df )
  df <- df[ ! grepl( "$^", df$V2 ) , ]
  
  return( df )
}

el <- create_edgelist( xpaths.t2 )


doc <- xml2::read_xml( grady )
nodeset <- xml2::xml_children( doc ) # top level nodeset
xpaths.grady <- xmltools::xml_get_paths( doc ) %>% unlist() %>% unique()
xpaths.grady <- gsub( "/GRADY/", "GRADY/", xpaths.grady )
el <- create_edgelist( xpaths.grady )
```




```{r, fig.height=8, fig.width=8}
library( igraph )
g <- graph_from_data_frame( d=el, directed=TRUE, vertices=NULL )
plot( g, layout=layout_as_tree )
```







```{r}
library( data.tree )
nd <- FromDataFrameNetwork( network=el )
print( nd )
```


```{r, fig.width=10}
SetGraphStyle( nd, rankdir = "TB")
SetEdgeStyle( nd, arrowhead = "vee", color = "grey20", penwidth = 2 )
SetNodeStyle( nd, 
              style = "filled,rounded", 
              shape = "box", 
              fillcolor = "LightBlue", 
              fontname = "helvetica", 
              fontcolor="black",
              tooltip = GetDefaultTooltip )

# SetNodeStyle(acme$IT, fillcolor = "LightBlue", penwidth = "5px")
plot( nd )
```


```{r, fig.width=10}
library(networkD3)
net <- ToDataFrameNetwork( nd, "name" )
simpleNetwork( net[-3], fontSize = 12 )
```


```{r}
el <- create_edgelist( xpaths.t2 )
nd <- FromDataFrameNetwork( network=el )
net <- ToDataFrameNetwork( nd, "name" )
simpleNetwork( el, fontSize = 12 , linkDistance = 25, charge = -100 )
```












```{r, eval=F, echo=F}
#' view xml simliar to the unix tree command line tool
#' @param xml an object of class "xml_nodeset" or "xml_document"
#' @param depth how deep to go. root is 0, next is 1, etc. NULL by default.
#' @export
xml_view_trees <- function(xml, depth = NULL) {

  stopifnot(any(c("xml_tree", "xml_tree_list", "xml_document", "xml_nodeset") %in% class(xml)))

  if(any(c("xml_nodeset","xml_document") %in% class(xml))) {
    xml <- xml_get_trees(xml, depth = depth)
  } else {
    if(!is.null(depth)) warning("Option `depth` is ignored for xml_tree and xml_tree_objects.")
  }

  if("xml_tree" %in% class(xml)) {
    out <- paste(xml, collapse = "\n")
    cat(out, "\n")
    invisible()
  }

  if("xml_tree_list" == class(xml)) {
    out <- lapply(xml, paste, collapse = "\n")
    if(length(xml) > 1) {
      out <- paste("\n\n", paste0("(",seq_along(out),")"), "------------\n\n", out)
    } else {
      out <- paste(out)
    }
    cat(out, sep = "\n")
    invisible()
  }

}

#' @export
xml_view_tree <- function(xml, depth = NULL) xml_view_trees(xml, depth = depth)

#' get a tree of xml simliar to the unix tree command line tool
#' @param doc an xml doc or nodeset
#' @param depth how deep to go. root is 0, next is 1, etc. NULL by default.
xml_get_trees <- function(doc, depth = NULL) {

  stopifnot(any(c("xml_document", "xml_nodeset") %in% class(doc)))

  if("xml_document" %in% class(doc)) {
    root <- xml2::xml_root(doc)
    nodeset <- xml2::xml_children(root)
  }

  if("xml_nodeset" %in% class(doc)) nodeset <- doc

  tree <- tree_dig(nodeset, depth, counter = 1) %>%
    parse_tree()
  tree <- lapply(tree, structure, class = "xml_tree")
  tree <- structure(tree, class = "xml_tree_list")

  return(tree)
}

xml_get_tree <- function(doc, depth = NULL) xml_get_trees(doc, depth = NULL)

tree_dig <- function(nodeset, depth, counter = 1) {

  if(!is.null(depth)) {
    if(counter > depth) return()
  }

  node_len <- nodeset %>%
    xml2::xml_length()

  # top level are nodes with ln == 0
  terminal <- node_len == 0

  x <- nodeset %>%
      xml2::xml_name() %>% # get all node names
      paste(counter, "?????????", .)

  if(sum(terminal) == 0) { # no top level data
      x[length(x)] <- gsub("?????????","?????????", x[length(x)]) # mark the last branch
      nodeset <- lapply(nodeset, xml2::xml_children)
      mapply(function(i, j) append(list(i), tree_dig(j, depth, counter + 1)),
        i = x, j = nodeset, USE.NAMES = FALSE, SIMPLIFY = FALSE)
  } else {
    if(sum(terminal) == length(terminal)) {
      x <- x[terminal] # subset to only terminal nodes
      x[length(x)] <- gsub("?????????","?????????", x[length(x)]) # mark the last branch
      return(x)
    } else {
      y <- x[terminal] # get terminal nodes
      x <- x[!terminal] # get non terminal nodes
      x[length(x)] <- gsub("?????????","?????????", x[length(x)]) # mark the last branch
      nodeset <- nodeset[!terminal]
      nodeset <- lapply(nodeset, xml2::xml_children)
      append(list(y), mapply(function(i, j)
        append(list(i), tree_dig(j, depth, counter + 1)),
        i = x, j = nodeset, USE.NAMES = FALSE, SIMPLIFY = FALSE))
    }
  }
}

parse_tree <- function(tree) {
  trees <- lapply(tree, unlist) %>%
    lapply(. %>% add_padding())
  return(trees)
}

add_padding <- function(x) {

  padding <- function(p) paste(rep("  ", p-1), collapse = "")

  m <- regexpr('^[0-9]', x)
  num <- regmatches(x, m) %>%
    as.integer()
  x <- gsub('^[0-9] ', '', x)

  paste0(sapply(num, padding), x)

}

xml_get_trees( doc )
```



```{r, eval=F, echo=F}
# to better understand recursive xml for later
doc <- XML::xmlParse( grady )
nodes <- XML::getNodeSet( doc, "//GRADY/HospitalFacilitiesGrp" )

flatten_xml <- function(x) {
  if ( length(xmlChildren(x) ) == 0 ) 
    {
      structure( list( xmlValue(x) ), .Names=xmlName( xmlParent(x) ) )
    } else Reduce( append, lapply( xmlChildren(x), flatten_xml ) )
}

dfs <- lapply( nodes, function(x) data.frame(flatten_xml(x)) )
allnames <- unique(c(lapply(dfs, colnames), recursive = TRUE))
df <- do.call(rbind, lapply(dfs, function(df) { df[, setdiff(allnames,colnames(df))] <- NA; df }))
head(df)
```


```{r, eval=F, echo=F}
function (xml, depth = NULL) 
{
  stopifnot(any(c("xml_tree", "xml_tree_list", "xml_document", 
    "xml_nodeset") %in% class(xml)))
  if (any(c("xml_nodeset", "xml_document") %in% class(xml))) {
    xml <- xml_get_trees(xml, depth = depth)
  }
  else {
    if (!is.null(depth)) 
      warning("Option `depth` is ignored for xml_tree and xml_tree_objects.")
  }
  if ("xml_tree" %in% class(xml)) {
    out <- paste(xml, collapse = "\n")
    cat(out, "\n")
    invisible()
  }
  if ("xml_tree_list" == class(xml)) {
    out <- lapply(xml, paste, collapse = "\n")
    if (length(xml) > 1) {
      out <- paste("\n\n", paste0("(", seq_along(out), 
        ")"), "------------\n\n", out)
    }
    else {
      out <- paste(out)
    }
    cat(out, sep = "\n")
    invisible()
  }
}
```



```{r, eval=F, echo=F}
doc <- XML::xmlParse( grady )
nodes <- XML::getNodeSet( doc, "//GRADY/HospitalFacilitiesGrp" )

xmlData <- xmlInternalTreeParse( grady, useInternalNodes = TRUE)
xmltop = xmlRoot( xmlData )
nodes <- getNodeSet( xmltop, '//GRADY', namespaces = c(as=xmlNamespace(xmltop)))
df <- xmlToDataFrame(nodes)

xml_children( nodes )



XML::xmlTreeParse( grady )
              
XML::xmlTree( "GRADY", doc )
xmlDoc( )

library(data.tree)

SetGraphStyle(acme, rankdir = "TB")
SetEdgeStyle(acme, arrowhead = "vee", color = "grey35", penwidth = 2)
SetNodeStyle(acme, style = "filled,rounded", shape = "box", fillcolor = "GreenYellow", 
            fontname = "helvetica", tooltip = GetDefaultTooltip)
SetNodeStyle(acme$IT, fillcolor = "LightBlue", penwidth = "5px")
plot(acme)
```






```{r, eval=F, echo=F}


listn <- function(...) {
  objs <- as.list(substitute(list(...)))[-1L]
  nm <- as.character(objs)
  v <- lapply(nm,get)
  names(v) <- nm
  return(v)
}


	namedList <- function(...){
		      names <- as.list(substitute(list(...)))[-1L]
		      result <- list(...)
		      names(result) <- names
		      result[sapply(result, function(x){length(x)==0})] <- NA
		      result[sapply(result, is.null)] <- NA
		      result
	}
	
	
ls <- as_list( xml_text(nodes) )
lapply( ls, xml_text )

lapply( nodes, xml_text )

lapply( xml_children(nodes), as_list )

as_list( nodes )

lapply( nodes, length )

nodenames <- xml_name( xml_children(nodes) )
nodevalues <- trimws( xml_text(xml_children(nodes)) )



lapply( nodes, function(x){xml_name(xml_children(x))} )

lapply( xml_children(doc), function(x) as.list( .name=xml_name(x),  ) )

 kids <- bind_rows( lapply( xml_children(doc), function(x) as.list( .name=xml_name(x),  ) ) )
 
 
 dat <- do.call( rbind, lapply(strsplit(vals, "\ +"),
                                 function(x) {
                                   data.frame(rbind(setNames(as.numeric(x),cols)))
                                 }))
```

```{r, eval=F, echo=F}
# library(purrr)
# library(stringr)
library( xml2 )

split_by <- function(.x, .f, ...) {
  vals <- map(.x, .f, ...)
  split(.x, simplify_all(transpose(vals)))
}

node_to_df <- function(node) {
  
    node <- doc
    ns <- xml2::xml_ns( doc )
    # Filter the attributes for ones that aren't namespaces
    # x <- list(.index = 0, .name = xml_name(node, ns))
    x <- list( .name = xml2::xml_name( node, ns ) )
    # Attributes as column headers, and their values in the first row
    attrs <- xml_attrs(node)
    if (length(attrs) > 0) {attrs <- attrs[!grepl("xmlns", names(attrs))]}
    if (length(attrs) > 0) {x <- c(x, attrs)}
    # Build data frame manually, to avoid as.data.frame's good intentions
    children <- xml2::xml_children(node)
    if (length(children) >= 1) {
      x <- 
        children %>%
        # Recurse here
        map( node_to_df ) %>%
        split_by( ".name" ) %>%
        map( bind_rows ) %>%
        map( list ) %>%
        {c(x, .)}
      attr(x, "row.names") <- 1L
      class(x) <- "data.frame"
    } else {
      x$.value <- xml_text( node )
    }
    x
}

node_to_df( doc )

xml_to_df <- function( doc, ns = xml_ns(doc) ) {

}


doc <- xml2::read_xml( grady )
df <- xml_to_df( doc  )

```


```{r, eval=F, echo=F}
xtrct <- function(doc, target) { xml_find_all(doc, target) %>% xml_text() %>% trimws() }

xtrct_df <- function( doc, top ) {
  xml_find_first( doc, sprintf("//%s", top) ) %>%
    xml_children() %>%
    xml_name() %>%
    map( ~{
      xtrct( doc, sprintf("//%s/%s", top, .x) ) %>%
        list() %>%
        set_names( tolower(.x) )
    }) %>%
    flatten_df() %>%
    readr::type_convert()
}


doc <- xml2::read_xml( grady )
xtrct_df( doc, top="GRADY" )

nodeset <- xml2::xml_children( doc ) # top level nodeset
```


